Adopting agile in the large: motivations, success factors and challenges

### 2013-01-25 tex/article.tex
Spellcheck

It is typical for large companies to function according to plan-driven software
engineering models. These models strive for consistent quality and performance
by rigorous planning and definition of process. This kind of approach is however
badly suited for software development, as projects typically encounter
situations that are too hard or impossible to foretell \citegen{Schwaber2002}.
The main problems in plan-driven development are the high cost of changes and
late feedback on quality \citegen{Petersen2010}. Long release cycles, cost of
resopnding to change and distance from customers undermine the  competitiveness
of companies. Agile methods are believed to bring remedy to these problems.

The goal of this research is to explore how and why large organizations adopt
agile methods. Studies on large scale agile transformations have been published,
but no extensive or summarizing research is available on the subject. In this
research we will give an overview of reported case studies on adopting agile
methods in large organizations. We will further discuss the motivations for
adopting agile methods, the characteristics of agile transformations, and
factors relating to success or challenge in the transformation process. Our
research is focused on the process of organizational change. We leave out topics
related to comparing the initial and transformed states of organisations, such
as measuring the performance of organizations before and after the
transformation.

@@

Analysis of the primary studies was guided by using a data extraction form with
open ended fileds. The reason for starting a transformation was captured in
fileds \textit{initial state of organization} and \textit{reasons for change}.
The description of the transformation process was captured in one field.
Recommendations for transformation processes were captured in fields
\textit{reported good practices}, \textit{reported challenges}, and
\textit{lessons learned}.
Additional fields that were used but not sufficiently answered by the primary
studies were \textit{satisfaction after transformation} and \textit{reported
measurements before/after transformation}.

@@

All of the included studies had been published within a decade. On average the
studies were published theree years after the transformation was reported to
have begun. Figure \ref{fig:publications} gives a timeline view of the
publications.

@@

\begin{table}[t]
    \begin{tabular}{ l@{ \hskip 0.4cm } l }
        \toprule
        Agile method    & Reported in number of studies   \\ \midrule
        Scrum           & 18 \\ 
        XP              & 7 \\
        Lean            & 5 \\
        Tailoring and combining methods & 9  (indirect mentionings not counted) \\
        \bottomrule
    \end{tabular}
    \caption{Reported use of agile methods}
    \label{table:methods}
\end{table}

@@

\begin{table}[t]
    \begin{tabular}{ l@{ \hskip 0.4cm } l }
        \toprule
        Reason                                    & In studies   \\ \midrule
        Need to improve performance               & S8, S11, S15, S16, S17, S24, S27 \\ 
        Need to improve time to market            & S6, S9, S13, S19, S24 \\
        Need to eliminate known process problems  & S5, S6, S10, S13, S19, S21 \\
        \bottomrule
    \end{tabular}
    \caption{Reported resasons for initiating a transformation}
    \label{table:motivations}
\end{table}

@@

It is difficult to make a new way of wroking stick in a large organization.
Use of agile can be rooted into the organization by creating an agile community.
Founding of interest groups and arranging regular seminars are good ways for
building community. As agility emphasizes people centricity and flexibility the
new ways of working can not be mandated. Instead, coaching should be applied for
leading the change. Several studies suggest conformity in the application of
agile models. Conformity avoids disorder when several teams are simultaneously
finding their agile ways.

>>>>

It is typical for large companies to function according to plan-driven software
engineering models. These models strive for consistent quality and performance
by rigorous planning and definition of process. This kind of approach is however
badly suited for software development, as projects typically encounter
situations that are too hard or impossible to foretell \citegen{Schwaber2002}.
The main problems in plan-driven development are the high cost of changes and
late feedback on quality \citegen{Petersen2010}. Long release cycles, cost of
responding to change and distance from customers undermine the  competitiveness
of companies. Agile methods are believed to bring remedy to these problems.

The goal of this research is to explore how and why large organizations adopt
agile methods. Studies on large scale agile transformations have been published,
but no extensive or summarizing research is available on the subject. In this
research we will give an overview of reported case studies on adopting agile
methods in large organizations. We will further discuss the motivations for
adopting agile methods, the characteristics of agile transformations, and
factors relating to success or challenge in the transformation process. Our
research is focused on the process of organizational change. We leave out topics
related to comparing the initial and transformed states of organizations, such
as measuring the performance of organizations before and after the
transformation.

@@

Analysis of the primary studies was guided by using a data extraction form with
open ended fields. The reason for starting a transformation was captured in
fields \textit{initial state of organization} and \textit{reasons for change}.
The description of the transformation process was captured in one field.
Recommendations for transformation processes were captured in fields
\textit{reported good practices}, \textit{reported challenges}, and
\textit{lessons learned}.
Additional fields that were used but not sufficiently answered by the primary
studies were \textit{satisfaction after transformation} and \textit{reported
measurements before/after transformation}.

@@

All of the included studies had been published within a decade. On average the
studies were published three years after the transformation was reported to
have begun. Figure \ref{fig:publications} gives a timeline view of the
publications.

@@

\begin{table}[t]
    \begin{tabular}{ l@{ \hskip 0.4cm } l }
        \toprule
        Agile method    & Reported in number of studies   \\ \midrule
        Scrum           & 18 \\ 
        XP              & 7 \\
        Lean            & 5 \\
        Tailoring and combining methods & 9  (indirect mentioning not counted) \\
        \bottomrule
    \end{tabular}
    \caption{Reported use of agile methods}
    \label{table:methods}
\end{table}

@@

\begin{table}[t]
    \begin{tabular}{ l@{ \hskip 0.4cm } l }
        \toprule
        Reason                                    & In studies   \\ \midrule
        Need to improve performance               & S8, S11, S15, S16, S17, S24, S27 \\ 
        Need to improve time to market            & S6, S9, S13, S19, S24 \\
        Need to eliminate known process problems  & S5, S6, S10, S13, S19, S21 \\
        \bottomrule
    \end{tabular}
    \caption{Reported reasons for initiating a transformation}
    \label{table:motivations}
\end{table}

@@

It is difficult to make a new way of working stick in a large organization.
Use of agile can be rooted into the organization by creating an agile community.
Founding of interest groups and arranging regular seminars are good ways for
building community. As agility emphasizes people centricity and flexibility the
new ways of working can not be mandated. Instead, coaching should be applied for
leading the change. Several studies suggest conformity in the application of
agile models. Conformity avoids disorder when several teams are simultaneously
finding their agile ways.
